---
title: "R Notebook"
output: html_notebook
---

```{r}
a = sqrt(3)
b = 1/4 
c = 11 
w = 1/2
```



```{r}
"
rungekutta = function(f,t0,y0,h,n){
  t = seq(t0, t0+n*h, by=h)
  y = rep(NA, times=(n+1))
  
  y[1] = y0
  for(k in 2:(n+1)){
    k1=h/2*f(t[k-1],y[k-1])
    k2=h/2*f(t[k-1]+h/2, y[k-1]+k1)
    k3=h/2*f(t[k-1]+h/2, y[k-1]+k2)
    k4=h/2*f(t[k-1]+h, y[k-1]+2*k3)
    y[k] = y[k-1]+1/3*(k1+2*k2+2*k3+k4)
  }
  return(data.frame(X = t, Y = y))
}
"

rungekutta = function(f,t0,y0,h,n){
  t = seq(t0, t0+n*h, by=h)
  y = rep(NA, times=(n+1))
  # length(t)==length(y)
  y[1] = y0
  for(k in 2:(n+1)){
    k1=h/2*f(t[k-1],y[k-1])
    k2=h/2*f(t[k-1]+h/2, y[k-1]+k1)
    k3=h/2*f(t[k-1]+h/2, y[k-1]+k2)
    k4=h/2*f(t[k-1]+h, y[k-1]+2*k3)
    y[k] = y[k-1]+1/3*(k1+2*k2+2*k3+k4)
  }
  dat = cbind(t,y)
  print(as.matrix(dat))
  plot(t,y,pch=20, col="red")
}

euler1 = function(f, t0, y0, h, n) {
  #Datos igualmente espaciados iniciando en x0 = a, paso h. "n" datos
  t = seq(t0, t0 + (n-1)*h, by = h) # n datos
  y = rep(NA, times=n)
  # n datos
  y[1]=y0
  for(i in 2:n ) y[i]= y[i-1]+h*f(t[i-1], y[i-1])
  print(cbind(t,y))
  # print
  plot(t,y, pch=19, col="red")
  # gráfica
}

graficar<-function(e1, col="red"){
  i=1
  while(i<=nrow(e1))
  {
    lines(e1$X, e1$Y, col=col)
    i = i+1
  }
}

```


```{r}

a = sqrt(3)
b = 1/4 
c = 11 
w = 1/2

# falta modificar esta funcion 
f = function(x,y) 1-x^2+(x+y)

t0 = 0; y0 = 1; 

# punto 1 
h = 0.1
rungekutta(f, t0,y0,h,20)
h = 0.2
rungekutta(f, t0,y0,h,20)




# punto 2 

b = 1/4
ff <- function(x,y) { 3*x - b*y }
ff2<- function(x,y) { 5*x - 4*y }

x0 <- 3
y0 <- 6

x = 7.5
y = -9

x <-  ff(x0,y0)
y <- ff2(x0,y0)

print("euler: ")
euler1( f , ff(x0,y0) , ff2(x0,y0) ,h ,10 )

x <- c()
y <- c()

for( i in 0:10)
{
  x <- c(x, ff(x0 + i,y0 + i  ) )
  y <- c(y, ff2(x0 + i,y0 + i))

}
print("real: ")
print(x)

#plot( ,type="l",asp=1)


lines( x , y, col = 3)


    

```


```{r}

euler1 <- function(f,f2,t0, y0, h, n) 
{
  #Datos igualmente espaciados iniciando en x0 = a, paso h. "n" datos t = seq(t0, t0 + (n-1)*h, by = h) # n datos
  y = rep(NA, times=n) # n datos
  y[1]=y0
  x = rep(NA, times=n) # n datos
  x[1]=t0
  t <- c()
  for(i in 2:n ) x[i]= x[i-1]+h*f(t[i-1], x[i-1])
  for(i in 2:n ) y[i]= y[i-1]+h*f2(t[i-1], y[i-1])
  print(cbind(t,y)) # print
  plot(t,y, pch=19, col="red") # gráfica
}

xprima = function(x,y) 3*x-0.2*y

yprima <- function(x,y) 5*x-4*y

n=10
x0=3
y0=6
h=0.1


euler1(xprima,yprima,x0, y0,h,n)

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
